\documentclass[12pt]{article}
\usepackage{amsmath} % for 'bmatrix' environmen
\usepackage{commath}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[document]{ragged2e}
\begin{document}
    \section*{Question 1}
    \begin{flushleft}
        A ship travels with velocity given by
        $
            \begin{bmatrix}
                1 \\ 2
            \end{bmatrix}
        $
        , with current flowing in the direction given by 
        $
            \begin{bmatrix}
                1 \\ 1 
            \end{bmatrix}
        $
        with respect to some co-ordinate axes.
        \begin{flushleft}
            What is the velocity of the ship in the direction of the current?
        \end{flushleft}
    \end{flushleft}
    \subsection*{Answer}
    \begin{flushleft}
        $
            \text{vector projection} = r \frac{r \cdot s}{\abs{r}^2}
            = 2
        $ \\
        $
            \text{vector projection} = 
            \begin{bmatrix}
                1 \\ 1
            \end{bmatrix}
            *
            \frac{3}{2}
        $ \\
        $
            \boxed{
                \text{vector projection} =
                \begin{bmatrix}
                    3/2 \\ 3/2
                \end{bmatrix}
            }
        $
    \end{flushleft}

    \section*{Question 2}
    \begin{flushleft}
        A ball travels with velocity given by
        $
            \begin{bmatrix}
                2 \\ 1
            \end{bmatrix}
        $
        , with wind blowing in the direction given by
        $
            \begin{bmatrix}
                3 \\ -4
            \end{bmatrix}
        $
        with respect to some co-ordinate axes.
    \end{flushleft}
    \begin{flushleft}
        What is the size of the velocity of the ball in the direction of the wind?
    \end{flushleft}

    \subsection*{Answer}
    \begin{flushleft}
        This is a scalar projection problem because we are looking for size.
    \end{flushleft}
    \begin{flushleft}
        $
            \text{scalar projection} = \frac{r \cdot s}{\abs{r}}
        $ \\
        $
            \boxed{\text{scalar projection} = \frac{2}{5}}
        $
    \end{flushleft}

    \section*{Question 5}
    \begin{flushleft}
        At 12:00 pm, a spaceship is at position
        $
            \begin{bmatrix}
                3 \\ 2 \\ 4
            \end{bmatrix}
            km
        $
        away from the origin with respect to some 3 dimensional co ordinate system. The ship is travelling with velocity
        $
            \begin{bmatrix}
                -1 \\ 2 \\ -3
            \end{bmatrix}
            km/h.
        $
        What is the location of the spaceship after 2 hours have passed?
    \end{flushleft}
    \subsection*{Answer}
    \begin{flushleft}
        This problem is a simple vector addition problem. We know the speed of the spaceship. First, what we will do
        is multiply the speed in km/h by 2 to figure out the distance it will travel in 2 hours. \\
        $
            2
            \begin{bmatrix}
                -1 \\ 2 \\ -3
            \end{bmatrix}
            =
            \begin{bmatrix}
                -2 \\ 4 \\ -6
            \end{bmatrix}
            km/2h
        $
    \end{flushleft}
    \begin{flushleft}
        Now we can simply add the starting position + the distance in 2 hours the ship will travel. \\
        $
            \begin{bmatrix}
                3 \\ 2 \\ 4
            \end{bmatrix}
            +
            \begin{bmatrix}
                -2 \\ 4 \\ -6
            \end{bmatrix}
            =
            \boxed{
                \begin{bmatrix}
                    1 \\ 6 \\ -2
                \end{bmatrix}
                km
            }
        $
    \end{flushleft}
\end{document}